Binary companions of red giant stars in \apogee\ \DR

### 2018-03-04 paper/1-catalog/twoface-catalog.tex
Clarify

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when $P_{\textrm{max}} - P_{\textrm{min}}
< \Delta$ (see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior pdfs for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all columns in the high-$K$, unimodal sample catalog.

>>>>

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when $P_{\textrm{max}} - P_{\textrm{min}}
< \Delta$ (see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior pdfs for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} (MAP) sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
We additionally join with the \apogee\ \DR\ \texttt{allStar} catalog and provide
all columns from this catalog for convenience.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all
columns in the high-$K$, unimodal sample catalog, available online.
\todo{where?}
